%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}



%---------------------------------------------------------
\cventry
{\href{https://meld-ai.com/}{Landmarks Tracking Platform}} % Project Link
{MELD-AI} % Project Title
{University of Haifa \& Tech4Animals} % Project Scope
{2025} % Date(s)
{
\begin{cvitems}
\item {Migrated a \textbf{Django} video-tracking system to a \textbf{FastAPI} architecture, enabling each user to process up to \textbf{10 uploads/day} and handling \textbf{188+ total} inference jobs to date.}
\item {Designed and implemented FastAPI endpoints for video ingestion, preprocessing, and inference, achieving \textbf{4.45 min average latency.}}
\item {Led front-end redevelopment for real-time analytics UI, mentoring a dedicated developer on performance and usability best practices.}
\end{cvitems}
}
%---------------------------------------------------------
  \cventry
    {\href{https://github.com/ArielBubis/SONIC}{Rec-Sys Project}} % Project Link
    {SONIC: Cross-Modal Music Recommender System} % Project Title
    {} % Project Score: 96\%} % Location
    {2025} % Date(s)
    {
      \begin{cvitems}
            \item {Co-designed an end-to-end SONIC pipeline combining MFCC, DINO-ViT spectrogram embeddings, and multilingual lyric embeddings on 109K track Music4All dataset.}
            \item {Integrated BERT4Rec for sequential recommendation, achieving \textbf{80.65\% HitRate@50} and \textbf{outperforming baseline by 10\%}.}
        \end{cvitems}
    }

%---------------------------------------------------------
 
  \cventry
    {\href{https://github.com/Daniel-Himself/Dog-A-Eye}{B.Sc. Diploma Project}} % Job title
    {Dog-A-Eye: Canine Eye Imaging Tool} % Organization
    {} % Project Score: 95\%} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a React-based front end for intuitive canine eye image submission.}
        \item {Integrated a background YOLO service to preprocess and classify eye images automatically.}
        \item {Configured secure upload triggers to allow image transfers only after successful condition detection.}
      \end{cvitems}
    }

\end{cventries}