%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Journal of Veterinary Behavior (Elsevier)} % Journal
    {\href{https://www-sciencedirect-com.ezproxy.haifa.ac.il/science/article/pii/S155878782500125X}{Depth-Based Facial Proximity Modeling in Domestic Cats}} % Link
    {Peer-reviewed Article} % Scope
    {2026} % Date
    {
      \begin{cvitems}
        \item {Designed and implemented the full computer vision pipeline combining SAM (YOLO-seg), DepthAnything, and proximity estimation for facial interaction analysis in domestic cats.}
        \item {Built automated detection, segmentation, and depth-based distance computation workflows to extract fine-grained spatial proximity signals from video.}
        \item {Developed time-series representations and diagrams to model temporal dynamics of facial signaling and interaction patterns.}
        \item {Implemented preprocessing and feature extraction stages to support statistical analysis of context- and sex-based behavioral differences.}
        \item {Ensured robustness and reproducibility of the AI pipeline for integration into behavioral research workflows.}
      \end{cvitems}
    }


%---------------------------------------------------------
\cventry
    {Journal of Economic Entomology (Wiley)} % Journal
    {\href{https://onlinelibrary.wiley.com/doi/10.1111/jen.70009}{Morphology-Based Species Differentiation of Fruit Fly Larvae}} % Link
    {Peer-reviewed Article (Thesis)} % Scope
    {2025} % Date
    {
      \begin{cvitems}
        \item {Designed the dual-ellipse point representation to capture larval morphology and posture for species differentiation.}
        \item {Built the full computer vision pipeline for non-invasive larvae classification using video data.}
        \item {Curated and annotated the dataset (1,723 frames, 2,348 annotations) and segmented 9 raw videos into 1,632 fifteen-second clips.}
        \item {Trained YOLOv8 for larval detection and integrated representation features for downstream temporal modeling.}
        \item {Achieved \textbf{90.4\% accuracy}, \textbf{87.4\% specificity}, and \textbf{90.7\% F1-score} on a 327-video test set (\textbf{15\% above baseline}).}
      \end{cvitems}
    }

\end{cventries}
